---
title: "p8105_hw1_yl5221"
author: "Yuhuan Lin"
date: 2022-09-24
output: github_document
---

## Problem 1
```{r setup, include=FALSE}
library(palmerpenguins)
library(tidyverse)
```

```{r}
data("penguins", package = "palmerpenguins")
```

### Describing Penguins Data
The penguins data set contains 344 rows and 8 columns, including species, island, bill_length, bill_depth, flipper_length, body_mass, sex, and year. The mean of flipper_length is 200.9152.
```{r}
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

### scatterplot 
```{r}
g <- ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) + geom_point()
ggsave("plot.png", g, device=png)
```


## Problem 2

### Create Dataframe
```{r}
problem_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = (vec_numeric > 0),
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("male", "male", "female", "male", "male", "female", "female", "male", "female", "male"))
)
```

### Take Mean
We can get result of mean of numeric and logical vectors, but not for character and factor vectors. Mean function can only calculate results for numeric or logical variables.
```{r, warning=FALSE}
mean(problem_df$vec_numeric)
mean(problem_df$vec_logical)
mean(problem_df$vec_char)
mean(problem_df$vec_factor)
```

### As Numeric
The factor variable can be converted into numeric value but the character vector cannot. When we want to calculate mean for character and factor vectors, we need to see if they can be turned into numeric variables. The character vector isn't properly structured and cannot be translated into numeric class.
```{r echo=TRUE, results='hide', warning=FALSE}
num_char <- as.numeric(problem_df$vec_char)
num_fac <- as.numeric(problem_df$vec_factor)
```

